Democracy, Public Support, and Measurement Uncertainty

### 2021-07-31 paper/dcpo_demsupport.Rmd
update codes and comparison between supdem and exp_data. @sammo3182 please check whether the updated data is consistent with numberic description.

@@

## Incorporating Uncertainty

@@

Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty from the measurement model as well as outcome and control variables.
We take 900 draws from the distribution of public democratic support, duplicate each article's analysis dataset of variables without "measurement error" 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

```{r compare_n, eval = TRUE}
dcpo_input_raw1 <-
    read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>%
    filter(!(
        str_detect(survey, "army_wvs") &
            # WVS obs identified as problematic by Claassen
            ((country == "Albania" & year == 1998) |
                 (country == "Indonesia" &
                      (year == 2001 | year == 2006)) |
                 (country == "Iran" & year == 2000) |
                 (country == "Pakistan" &
                      (year == 1997 | year == 2001)) | # 1996 in Claassen
                 (country == "Vietnam" & year == 2001)
            ) |
            (str_detect(item, "strong_wvs") &
                 ((country == "Egypt" & year == 2012) |
                      (country == "Iran" &
                           (year == 2000 | year == 2007)) | # 2005 in Claassen
                      (country == "India") |
                      (country == "Pakistan" &
                           (year == 1997 | year == 2001)) | # 1996 in Claassen
                      (country == "Kyrgyzstan" &
                           (year == 2003 | year == 2011)) |
                      (country == "Romania" &
                           (year == 1998 | year == 2005 | year == 2012)) |
                      (country == "Vietnam" & year == 2001)
                 )) |
            (
                country %in% c(
                    "Puerto Rico",
                    "Northern Ireland",
                    "SrpSka Republic",
                    "Hong Kong SAR China"
                )
            )
    )) %>%
    DCPOtools::with_min_yrs(2)

@@

dcpo_input_nc <- dcpo_input_raw1 %>% 
  dplyr::select(country) %>% 
  distinct() %>% 
  nrow()

dcpo_input_surv <- dcpo_input_raw1 %>%
  dplyr::select(country, year, survey) %>%
  distinct() %>%
  separate(survey, c("surv1", "surv2"), sep=",", fill = "left") %>%
  pivot_longer(cols = starts_with("surv")) %>%
  filter(!is.na(value)) %>% 
  nrow()

dcpo_input_ncy <- dcpo_input_raw1 %>% 
  dplyr::select(country, year) %>% 
  distinct() %>% 
  nrow()

dcpo_input_ncyi <- dcpo_input_raw1 %>% 
  dplyr::select(country, year, item, survey) %>% 
  distinct() %>% 
  separate(survey, c("surv1", "surv2"), sep=",", fill = "left") %>%
  pivot_longer(cols = starts_with("surv")) %>%
  filter(!is.na(value)) %>% 
  nrow()

@@

<!-- This paragraph should be revised. -->
In addition to incorporating uncertainty, we expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index. 
We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018]. 
We drew 900 samples from the distribution of the Corruption Perception Index.^[Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.]

>>>>

load(here("data","claassen_replication_input.rda"))
load(here("data","exp_claassen_input.rda"))

@@

## Data Recollection and Incorporating Uncertainty
When we recollected the original data, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based @Claassen2020a's Dataverse materials.
It turned out that we have differences in number of country-year surveys and in sample size.
Specificially, our replication data has five fewer observations, three of which are no longer available in originial survey data and 2 seem to have never existed, and one more survey item which was conflated in original data [See more detail in Appendix].
<!-- which 5? South Sudan arabb4; Dominican Rep lb 2003; Spain lb 2005. 2? -->

@@

Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis model using our replication data.
We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty from the measurement model as well as outcome and control variables.
We take 900 draws from the distribution of public democratic support, duplicate each article's analysis dataset of variables without "measurement error" 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

```{r compare_n, eval = TRUE}

@@

dcpo_input_nc <- exp_claassen_input$data %>% 
  dplyr::select(country) %>% 
  distinct() %>% 
  nrow()

dcpo_input_surv <- exp_claassen_input$data %>%
  dplyr::select(country, year, survey) %>%
  distinct() %>%
  separate(survey, c("surv1", "surv2"), sep=",", fill = "left") %>%
  pivot_longer(cols = starts_with("surv")) %>%
  filter(!is.na(value)) %>% 
  nrow()

dcpo_input_ncy <- exp_claassen_input$data %>% 
  dplyr::select(country, year) %>% 
  distinct() %>% 
  nrow()

dcpo_input_ncyi <- exp_claassen_input$data %>% 
  dplyr::select(country, year, item, survey) %>% 
  distinct() %>% 
  separate(survey, c("surv1", "surv2"), sep=",", fill = "left") %>%
  pivot_longer(cols = starts_with("surv")) %>%
  filter(!is.na(value)) %>% 
  nrow()

@@

<!-- This paragraph should be revised. -->
We also expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index [See Appendix].

<!-- put it into memo rather than in main context. -->
We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018]. 
We drew 900 samples from the distribution of the Corruption Perception Index.^[Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.]
